### 2018-05-03 thread-pool-implementation/paper.tex
init doc

\documentclass[journal, a4paper]{IEEEtran}

% some very useful LaTeX packages include:

%\usepackage{cite}      % Written by Donald Arseneau
                        % V1.6 and later of IEEEtran pre-defines the format
                        % of the cite.sty package \cite{} output to follow
                        % that of IEEE. Loading the cite package will
                        % result in citation numbers being automatically
                        % sorted and properly "ranged". i.e.,
                        % [1], [9], [2], [7], [5], [6]
                        % (without using cite.sty)
                        % will become:
                        % [1], [2], [5]--[7], [9] (using cite.sty)
                        % cite.sty's \cite will automatically add leading
                        % space, if needed. Use cite.sty's noadjust option
                        % (cite.sty V3.8 and later) if you want to turn this
                        % off. cite.sty is already installed on most LaTeX
                        % systems. The latest version can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/cite/

\usepackage{graphicx}   % Written by David Carlisle and Sebastian Rahtz
                        % Required if you want graphics, photos, etc.
                        % graphicx.sty is already installed on most LaTeX
                        % systems. The latest version and documentation can
                        % be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/required/graphics/
                        % Another good source of documentation is "Using
                        % Imported Graphics in LaTeX2e" by Keith Reckdahl
                        % which can be found as esplatex.ps and epslatex.pdf
                        % at: http://www.ctan.org/tex-archive/info/

%\usepackage{psfrag}    % Written by Craig Barratt, Michael C. Grant,
                        % and David Carlisle
                        % This package allows you to substitute LaTeX
                        % commands for text in imported EPS graphic files.
                        % In this way, LaTeX symbols can be placed into
                        % graphics that have been generated by other
                        % applications. You must use latex->dvips->ps2pdf
                        % workflow (not direct pdf output from pdflatex) if
                        % you wish to use this capability because it works
                        % via some PostScript tricks. Alternatively, the
                        % graphics could be processed as separate files via
                        % psfrag and dvips, then converted to PDF for
                        % inclusion in the main file which uses pdflatex.
                        % Docs are in "The PSfrag System" by Michael C. Grant
                        % and David Carlisle. There is also some information
                        % about using psfrag in "Using Imported Graphics in
                        % LaTeX2e" by Keith Reckdahl which documents the
                        % graphicx package (see above). The psfrag package
                        % and documentation can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/psfrag/

%\usepackage{subfigure} % Written by Steven Douglas Cochran
                        % This package makes it easy to put subfigures
                        % in your figures. i.e., "figure 1a and 1b"
                        % Docs are in "Using Imported Graphics in LaTeX2e"
                        % by Keith Reckdahl which also documents the graphicx
                        % package (see above). subfigure.sty is already
                        % installed on most LaTeX systems. The latest version
                        % and documentation can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/subfigure/

\usepackage{url}        % Written by Donald Arseneau
                        % Provides better support for handling and breaking
                        % URLs. url.sty is already installed on most LaTeX
                        % systems. The latest version can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/other/misc/
                        % Read the url.sty source comments for usage information.

%\usepackage{stfloats}  % Written by Sigitas Tolusis
                        % Gives LaTeX2e the ability to do double column
                        % floats at the bottom of the page as well as the top.
                        % (e.g., "\begin{figure*}[!b]" is not normally
                        % possible in LaTeX2e). This is an invasive package
                        % which rewrites many portions of the LaTeX2e output
                        % routines. It may not work with other packages that
                        % modify the LaTeX2e output routine and/or with other
                        % versions of LaTeX. The latest version and
                        % documentation can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/sttools/
                        % Documentation is contained in the stfloats.sty
                        % comments as well as in the presfull.pdf file.
                        % Do not use the stfloats baselinefloat ability as
                        % IEEE does not allow \baselineskip to stretch.
                        % Authors submitting work to the IEEE should note
                        % that IEEE rarely uses double column equations and
                        % that authors should try to avoid such use.
                        % Do not be tempted to use the cuted.sty or
                        % midfloat.sty package (by the same author) as IEEE
                        % does not format its papers in such ways.

\usepackage{amsmath}    % From the American Mathematical Society
                        % A popular package that provides many helpful commands
                        % for dealing with mathematics. Note that the AMSmath
                        % package sets \interdisplaylinepenalty to 10000 thus
                        % preventing page breaks from occurring within multiline
                        % equations. Use:
%\interdisplaylinepenalty=2500
                        % after loading amsmath to restore such page breaks
                        % as IEEEtran.cls normally does. amsmath.sty is already
                        % installed on most LaTeX systems. The latest version
                        % and documentation can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% Other popular packages for formatting tables and equations include:

%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty which improves the
% LaTeX2e array and tabular environments to provide better appearances and
% additional user controls. array.sty is already installed on most systems.
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

% V1.6 of IEEEtran contains the IEEEeqnarray family of commands that can
% be used to generate multiline equations as well as matrices, tables, etc.

% Also of notable interest:
% Scott Pakin's eqparbox package for creating (automatically sized) equal
% width boxes. Available:
% http://www.ctan.org/tex-archive/macros/latex/contrib/supported/eqparbox/

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.

% Your document starts here!
\begin{document}

% Define document title and author
	\title{Thread Pool Implementation in C}
	\author{Jialin Li and Edward Hu}
	\maketitle

% Write abstract here
\begin{abstract}
	This is a short report on our thread pool performance.
\end{abstract}

% Each section begins with a \section{title} command
\section{Introduction}
	% \PARstart{}{} creates a tall first letter for this first paragraph
	\PARstart{T}{hread} is a basic unit of CPU utilization, it consists of program counter, register set, and its own stack. Compared to processes, threads are much more lighweight since virtual memory space remains the same during a thread switch, which is not true for process switch. However, even threads sometimes pose overhead that will affect the performance of the program. Initializing and cleaning threads can pose a certain amount of overhead. For an parallel application that creates and destroys a large number of threads that each only runs for a short time, the thread management mechanism can create unnecessary resource waste. Thread pool can be useful in this type of scenario as it reduces the complexity of thread management and the overhead involved in thread creation and cleaning.

% Main Part
\section{Motivation}
	We want to be able to implement a thread pool that is convinient to use. We aim to create a provide an interface that is easy for programmers to use. Thus we minimize the number of functions exposed to the programmers to maintain simplicity. We also want the performance of the thread pool to be reasonably more efficient than normal thread-based version. Thus we create several test cases to compare the performances in different implementations. We mainly focused on testing the performance difference in thread-based implementation and Goroutine-based version for certain types of jobs. Finally, we simply want to learn how to implement a thread pool and explore the drawbacks along with possible improvmetns.

\section{Goals and Expectation}
	The report can be written in \LaTeX{} or Microsoft Word, but \LaTeX{} is definitely preferred.
	Its appearance should be as close to this document as possible to achieve consistency in the proceedings.

	% You can cite a book or paper by using \cite{reference}.
	% The references will be defined at the end of this .tex file in the bibliography
	References should be cited as numbers, and should be ordered by their appearance (example: ``... as shown in \cite{HOP96}, ...'').
	Only references that are actually cited can be listed in the references section.
	The references' format should be evident from the examples in this text.

	References should be of academic character and should be published and accessible.
	Your advisor can answer your questions regarding literature research.
	You must cite all used sources.
	Examples of good references include text books and scientific journals or conference proceedings.
	If possible, citing internet pages should be avoided. In particular, Wikipedia is \emph{not} an appropriate reference in academic reports.
	Avoiding references in languages other than English is recommended.

	% You can reference tables and figure by using the \ref{label} command. Each table and figure needs to have a UNIQUE label.
	Figures and tables should be labeled and numbered, such as in Table~\ref{tab:simParameters} and Fig.~\ref{fig:tf_plot}.

	% This is how you define a table: the [!hbt] means that LaTeX is forced (by the !) to place the table exactly here (by h), or if that doesnt work because of a pagebreak or so, it tries to place the table to the bottom of the page (by b) or the top (by t).
	\begin{table}[!hbt]
		% Center the table
		\begin{center}
		% Title of the table
		\caption{Simulation Parameters}
		\label{tab:simParameters}
		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
		\begin{tabular}{|c|c|}
			% To create a horizontal line, type \hline
			\hline
			% To end a column type &
			% For a linebreak type \\
			Information message length & $k=16000$ bit \\
			\hline
			Radio segment size & $b=160$ bit \\
			\hline
			Rate of component codes & $R_{cc}=1/3$\\
			\hline
			Polynomial of component encoders & $[1 , 33/37 , 25/37]_8$\\
			\hline
		\end{tabular}
		\end{center}
	\end{table}

	% If you have questions about how to write mathematical formulas in LaTeX, please read a LaTeX book or the 'Not So Short Introduction to LaTeX': tobi.oetiker.ch/lshort/lshort.pdf

	% This is how you include a eps figure in your document. LaTeX only accepts EPS or TIFF files.
	\begin{figure}[!hbt]
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{plot_tf}
		% Create a subtitle for the figure.
		\caption{Simulation results on the AWGN channel. Average throughput $k/n$ vs $E_s/N_0$.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:tf_plot}
		\end{center}
	\end{figure}

\section{Filling this page}
	Gallia est omnis divisa in partes tres, quarum unam incolunt Belgae, aliam Aquitani, tertiam qui ipsorum lingua Celtae, nostra Galli appellantur. Gallos ab Aquitanis Garumna flumen, a Belgis Matrona et Sequana dividit. Horum omnium fortissimi sunt Belgae, propterea quod a cultu atque humanitate provinciae longissime absunt, minimeque ad eos mercatores saepe commeant atque ea quae ad effeminandos animos pertinent important, proximique sunt Germanis, qui trans Rhenum incolunt, quibuscum continenter bellum gerunt. Qua de causa Helvetii quoque reliquos Gallos virtute praecedunt, quod fere cotidianis proeliis cum Germanis contendunt, cum aut suis finibus eos prohibent aut ipsi in eorum finibus bellum gerunt. Eorum una, pars, quam Gallos obtinere dictum est, initium capit a flumine Rhodano, continetur Garumna flumine, Oceano, finibus Belgarum, attingit etiam ab Sequanis et Helvetiis flumen Rhenum, vergit ad septentriones. Belgae ab extremis Galliae finibus oriuntur, pertinent ad inferiorem partem fluminis Rheni, spectant in septentrionem et orientem solem.

\section{Conclusion}
	This section summarizes the paper.

% Now we need a bibliography:
\begin{thebibliography}{5}

	%Each item starts with a \bibitem{reference} command and the details thereafter.
	\bibitem{HOP96} % Transaction paper
	J.~Hagenauer, E.~Offer, and L.~Papke. Iterative decoding of binary block
	and convolutional codes. {\em IEEE Trans. Inform. Theory},
	vol.~42, no.~2, pp.~429–-445, Mar. 1996.

	\bibitem{MJH06} % Conference paper
	T.~Mayer, H.~Jenkac, and J.~Hagenauer. Turbo base-station cooperation for intercell interference cancellation. {\em IEEE Int. Conf. Commun. (ICC)}, Istanbul, Turkey, pp.~356--361, June 2006.

	\bibitem{Proakis} % Book
	J.~G.~Proakis. {\em Digital Communications}. McGraw-Hill Book Co.,
	New York, USA, 3rd edition, 1995.

	\bibitem{talk} % Web document
	F.~R.~Kschischang. Giving a talk: Guidelines for the Preparation and Presentation of Technical Seminars.
	\url{http://www.comm.toronto.edu/frank/guide/guide.pdf}.

	\bibitem{5}
	IEEE Transactions \LaTeX and Microsoft Word Style Files.
	\url{http://www.ieee.org/web/publications/authors/transjnl/index.html}

\end{thebibliography}

% Your document ends here!
\end{document}

### 2018-05-03 thread-pool-implementation/paper.tex
progress on report

@@
 \documentclass[journal, a4paper]{IEEEtran}
-
-% some very useful LaTeX packages include:
-
-%\usepackage{cite}      % Written by Donald Arseneau
-                        % V1.6 and later of IEEEtran pre-defines the format
-                        % of the cite.sty package \cite{} output to follow
-                        % that of IEEE. Loading the cite package will
-                        % result in citation numbers being automatically
-                        % sorted and properly "ranged". i.e.,
-                        % [1], [9], [2], [7], [5], [6]
-                        % (without using cite.sty)
-                        % will become:
-                        % [1], [2], [5]--[7], [9] (using cite.sty)
-                        % cite.sty's \cite will automatically add leading
-                        % space, if needed. Use cite.sty's noadjust option
-                        % (cite.sty V3.8 and later) if you want to turn this
-                        % off. cite.sty is already installed on most LaTeX
-                        % systems. The latest version can be obtained at:
-                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/cite/
 
@@
                         % at: http://www.ctan.org/tex-archive/info/
-
+\usepackage{xcolor}
 %\usepackage{psfrag}    % Written by Craig Barratt, Michael C. Grant,
@@
 
-\usepackage{amsmath}    % From the American Mathematical Society
-                        % A popular package that provides many helpful commands
-                        % for dealing with mathematics. Note that the AMSmath
-                        % package sets \interdisplaylinepenalty to 10000 thus
-                        % preventing page breaks from occurring within multiline
-                        % equations. Use:
-%\interdisplaylinepenalty=2500
-                        % after loading amsmath to restore such page breaks
-                        % as IEEEtran.cls normally does. amsmath.sty is already
-                        % installed on most LaTeX systems. The latest version
-                        % and documentation can be obtained at:
-                        % http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
+\usepackage{amsmath}
+\usepackage{listings}
+
+\lstset{language=C}
 
@@
 Thread pool can be useful in this type of scenario as it reduces the complexity of thread management and the overhead involved in thread creation and cleaning.
+The thread pool in implement in \textbf{GNU C}.
 
@@
 We mainly focused on testing the performance difference in thread-based implementation and Goroutine-based version for certain types of jobs.
-Finally, we simply want to learn how to implement a thread pool and explore the drawbacks along with possible improvmetns.
+Finally, we simply want to learn how to implement a thread pool and explore the drawbacks along with possible improvmetns.\\
 
-\section{Goals and Expectation}
-	The report can be written in \LaTeX{} or Microsoft Word, but \LaTeX{} is definitely preferred.
-	Its appearance should be as close to this document as possible to achieve consistency in the proceedings.
+	There are several goals we are aiming to achieve in the experiment.
+First, we want to run both long and short tasks in the threal pool to analyze which type of tests have the most impact on the performance on the program.
+We've created created various tests for the thread pool to perform and we will show the data collected later in the analysis section.
+We hope the low overhead of switch between tasks will help us outperform thread-based implementation as well go-based implementation.
+In addition, we implemented work stealing mechanism to improve the work throughput done by the thread pool.
+We hope the work stealing function will further improve the efficiency of the thread pool.
 
-	% You can cite a book or paper by using \cite{reference}.
-	% The references will be defined at the end of this .tex file in the bibliography
-	References should be cited as numbers, and should be ordered by their appearance (example: ``... as shown in \cite{HOP96}, ...'').
-	Only references that are actually cited can be listed in the references section.
-	The references' format should be evident from the examples in this text.
+\section{Programming Interface}
+The programming interface is designed for simplicity, there are three functions users are exposed to.\\
 
-	References should be of academic character and should be published and accessible.
-	Your advisor can answer your questions regarding literature research.
-	You must cite all used sources.
-	Examples of good references include text books and scientific journals or conference proceedings.
-	If possible, citing internet pages should be avoided. In particular, Wikipedia is \emph{not} an appropriate reference in academic reports.
-	Avoiding references in languages other than English is recommended.
+\begin{itemize}
+	\item \begin{lstlisting}
+void thread_pool_init(int workers, 
+		      int mutex_flag);
+	\end{lstlisting}
+	This function initialize a new thread pool.
+The \textbf{workers} attribute specifies the number of threads that can exist in a thread pool.
+If $0$ is passd in, the number of threads will be initialized to the number of core in the execution environment.
+The \textbf{mutex\_flag} argument let user decides whether to use mutex or spinlock as synchronization method.
+Note if the thread pool is initialized more than once, every invocation of this function will be discarded.\\
+	\item 
+	\begin{lstlisting}
+bool thread_pool_add(task_func *func,
+		     void* aux,
+		     enum CallType);
+	\end{lstlisting}
+	This function adds tasks to the thread pool.
+The \textbf{func} attribute represents the function that is to be executed.
+The \textbf{aux} attribute indicates the parameter \textbf{func} takes in.
+the \textbf{CallType} specifies whether to use blocking or non-blocking mechanism for the thread pool.
+If a task is added without failure, $true$ is returned.
+Otherwise, $false$ will be returned.\\
+	\item \begin{lstlisting}
+void thread_pool_wait();
+	\end{lstlisting}
+	This function signifies all threads in thread pool that no more job will be added and the calling function waits for all tasks in the thread pool to finish.
+\end{itemize}
 
-	% You can reference tables and figure by using the \ref{label} command. Each table and figure needs to have a UNIQUE label.
-	Figures and tables should be labeled and numbered, such as in Table~\ref{tab:simParameters} and Fig.~\ref{fig:tf_plot}.
+\section{Implementation}
+The low overhead of the thread pool is acheived with several design decisions.
+We will discuss the major implementations.
+A thread pool is first initialized by the main thread and the corresponding number of threads are initialized with their attributes.
+Each task is represented as a \textbf{struct task}.
+It is created by the calling function whenever the user sends the function to be executed to the thread pool.
+It is then distributed to the threads in the thread pool in a round-robin style to ensure even distribution.
+Each thread owns a privat task queue to store all its assigned tasks.
+Each queue is protected by either a mutex or a spinlock depending on users' specification.
+However, it is possible that a thread's task queue is empty when it is first initialized.
+It will waste CPU resource if such task is kept up and running without executing any tasks.
+Thus, we use semaphore to improve the efficiency of the thread pool.
+Thus we let the main thread invoking sema\_post on each thread once it finishes adding tasks to the thread's task queue to indicate the availability of tasks.
+However, the thread's task queue can be empty for other reasons.
+The most important one is that the thread finishes executing all assigned tasks.
+Thus, we implement work stealing algorithm to keep the idle thread busy by letting it trying to steal tasks from other threads by randomly choosing one.
+Since we don't want tasks stealing to create too much overhead as it tries to grab tasks from other threads, we simply let the idle thread using pthread\_mutex\_trylock() or pthread\_spin\_trylock().
+If the stealing succeeds, the tasks is grabbed from the victim's task queue and executed.
+Otherwise, the steal will fail.
+If the steal fails too many times, that indicates many threads' task queue is already empty and the thread pool is getting close to running out of tasks.
+In this case, letting more threads trying to steal tasks will create unnecessary overhead, thus the thread will be blocked to prevent wasting resources.
+If eventually the threads run out of tasks, it will increase \textbf{wait\_sema} to let the main thread know it finishes its job.
+If all threads signify that they've finihsed their tasks, then thread pool is terminated.
+
+\section{Analysis}
 
 	% This is how you define a table: the [!hbt] means that LaTeX is forced (by the !) to place the table exactly here (by h), or if that doesnt work because of a pagebreak or so, it tries to place the table to the bottom of the page (by b) or the top (by t).
-	\begin{table}[!hbt]
+	%\begin{table}[!hbt]
 		% Center the table
-		\begin{center}
-		% Title of the table
-		\caption{Simulation Parameters}
-		\label{tab:simParameters}
+	%\begin{center}
+	%	\caption{Simulation Parameters}
+	%	\label{tab:simParameters}
 		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
-		\begin{tabular}{|c|c|}
-			% To create a horizontal line, type \hline
-			\hline
-			% To end a column type &
-			% For a linebreak type \\
-			Information message length & $k=16000$ bit \\
-			\hline
-			Radio segment size & $b=160$ bit \\
-			\hline
-			Rate of component codes & $R_{cc}=1/3$\\
-			\hline
-			Polynomial of component encoders & $[1 , 33/37 , 25/37]_8$\\
-			\hline
-		\end{tabular}
-		\end{center}
-	\end{table}
+	%	\begin{tabular}{|c|c|}
+	%		% To create a horizontal line, type \hline
+	%		\hline
+	%		% To end a column type &
+	%		% For a linebreak type \\
+	%		Information message length & $k=16000$ bit \\
+	%		\hline
+	%		Radio segment size & $b=160$ bit \\
+	%		\hline
+	%		Rate of component codes & $R_{cc}=1/3$\\
+	%		\hline
+	%		Polynomial of component encoders & $[1 , 33/37 , 25/37]_8$\\
+	%		\hline
+	%	\end{tabular}
+	%	\end{center}
+	%\end{table}
 

### 2018-05-03 thread-pool-implementation/paper.tex
more push

@@
 \section{Analysis}
+Below is the hardware we used to conduct experiements on the performance of the thread pool.
+	\begin{table}[!hbt]
+		% Center the table
+	\begin{center}
+		\caption{Hardware Sepcification}
+		\label{tab:simParameters}
+		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
+		\begin{tabular}{|c|c|}
+			% To create a horizontal line, type \hline
+			\hline
+			% To end a column type &
+			% For a linebreak type \\
+			Processor & Intel® Core™ i7-6700 CPU \\
+								&@3.40GHz $\times$ 8\\
+			\hline
+			RAM & $15.6$ GiB \\
+			\hline
+			OS & Ubuntu 16.04.4 LTS 64-bit\\
+			\hline
+		\end{tabular}
+		\end{center}
+	\end{table}
+
+We create same tasks for every implementation to execute to ensure fairness. we've tested(need some work here)...
+
+\section{Conclusion}
 
@@
 
-\section{Filling this page}
-	Gallia est omnis divisa in partes tres, quarum unam incolunt Belgae, aliam Aquitani, tertiam qui ipsorum lingua Celtae, nostra Galli appellantur.
-Gallos ab Aquitanis Garumna flumen, a Belgis Matrona et Sequana dividit.
-Horum omnium fortissimi sunt Belgae, propterea quod a cultu atque humanitate provinciae longissime absunt, minimeque ad eos mercatores saepe commeant atque ea quae ad effeminandos animos pertinent important, proximique sunt Germanis, qui trans Rhenum incolunt, quibuscum continenter bellum gerunt.
-Qua de causa Helvetii quoque reliquos Gallos virtute praecedunt, quod fere cotidianis proeliis cum Germanis contendunt, cum aut suis finibus eos prohibent aut ipsi in eorum finibus bellum gerunt.
-Eorum una, pars, quam Gallos obtinere dictum est, initium capit a flumine Rhodano, continetur Garumna flumine, Oceano, finibus Belgarum, attingit etiam ab Sequanis et Helvetiis flumen Rhenum, vergit ad septentriones.
-Belgae ab extremis Galliae finibus oriuntur, pertinent ad inferiorem partem fluminis Rheni, spectant in septentrionem et orientem solem.
-
 \section{Conclusion}

### 2018-05-03 thread.c
edit Makefilee

@@ -240,33 +240,15 @@ bool steal_work(Thread *t, unsigned int *seed) {
 void* worker_func(void* t) {
   int e;
   Thread* thread = (Thread*) t;
-  //printf("thread %li\n", thread->tid);
+
   unsigned int seed;
   /* grabbing a task from the front of the queue
      assume task is present */
   while(1) {
-    // NOTE: need to consider the interaction of sem_wait and 
-    // future work stealing algorithm
-
-    // ummm work stealing is gonna be weird lol
-    // but whatever, it will be fine.
-
-    /* try to get a task */
-    //if ((e=sem_trywait(&thread->task_sema)) != 0) {
-    //  printf("Failed to wait for task, error %d, will keep trying \n", errno);
-    //  continue;
-    //}
-  
-
-    // if we failed to decrement the semaphore,
-    // that is, we failed to gain the resource to execuet
-    // the task
-    // if no tasks exists
-int times = 0;
+    int times = 0;
     if (sem_trywait(&thread->task_sema) != 0) {
       int i = 0;
       while (true) {
-      //for (; i < workers/ 2; i++) {
       bool succeed = steal_work(thread, &seed);
         if (succeed) {
           // use try lock if possible
@@ -280,37 +262,17 @@ int times = 0;
       sem_wait(&thread->task_sema);
     } 
 
+    // execute tasks on its own private queue
     Task* task = NULL;
     lock(thread);
     if (thread->queue.num_tasks == 0 && thread->count > 0) 
     {
-      // wait for global signal send by the main thread
-      //if (global_stop == 1) { // check if atomic varible here works
         sem_post(&thread->wait_sema); /* indicates finishing execution */
-        //printf("finished\n\n");
-        break;
-      //}
     } else {
-//<<<<<<< HEAD
       task = thread->queue.start;
       thread->queue.num_tasks--;
       thread->queue.start = task->next;
       task->prev = NULL;
-  /*  if (thread->queue.num_tasks == 0) {
-      thread->count++;
-      thread->queue.end = NULL;
-    } else {
-      if (thread->queue.num_tasks > thread->max) 
-      	thread->max = thread->queue.num_tasks;
-    }*/
-
-
-      // maybe try random stealing here
-/*=======
-    task = thread->queue.start;
-    thread->queue.num_tasks--;
-    thread->queue.start = task->next;
->>>>>>> 05fe20000289860ff2caeeb697cd3cdcac5c2508 */
     }
     unlock(thread);
     

### 2018-05-03 thread-pool-implementation/paper.tex
add one pic

@@
 
-We create same tasks for every implementation to execute to ensure fairness. we've tested(need some work here)...
+We create same tasks for every implementation to execute to ensure fairness.
+we've selected three types of tests that represent three typical scenarios in most applications.
+We designed a task that accesses file system and performs read and write operations.
+Since accessing file system usually requires blocking which generates large overhead, this task is perfect to represent tasks that takes more than a few CPU cycles to finish.
+We also designed a task that task an argument, and then computer then sum based on the input and generates a simple hash value.
+This represents a short to medium tasks present in most applications and we selected it as a candidate to represent short tasks.
+We also include a task that does nothing in order to test sheer performance of the thread pool without the influence of any outside factors.
+In addition, we mixed the number of long and shorts tasks in each benchmark in order to generalize the real life scenario where a mixture of different tasks are executed.
+We want to show that the speedup is not or at least minimally affected by the type of tasks executed.\\
+
+\begin{figure}[!hbt]
+		% Center the figure.
+		\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{test_1.png}
+		% Create a subtitle for the figure.
+		\caption{Benchmark speedup using long blocking tasks and short tasks.
+From left to right each section represents: long 25\% with short 75\%, long 50\% with short 50\%, and long 75\% with short 25\%.
+Green bar: pthread per task.
+Blue: Thread pool.
+Yellow: pthread per core.
+Dark Green: Goroutines}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:tf_plot}
+		\end{center}
+	\end{figure}
 
 \section{Conclusion}
-
-	% This is how you define a table: the [!hbt] means that LaTeX is forced (by the !) to place the table exactly here (by h), or if that doesnt work because of a pagebreak or so, it tries to place the table to the bottom of the page (by b) or the top (by t).
-	%\begin{table}[!hbt]
-		% Center the table
-	%\begin{center}
-	%	\caption{Simulation Parameters}
-	%	\label{tab:simParameters}
-		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
-	%	\begin{tabular}{|c|c|}
-	%		% To create a horizontal line, type \hline
-	%		\hline
-	%		% To end a column type &
-	%		% For a linebreak type \\
-	%		Information message length & $k=16000$ bit \\
-	%		\hline
-	%		Radio segment size & $b=160$ bit \\
-	%		\hline
-	%		Rate of component codes & $R_{cc}=1/3$\\
-	%		\hline
-	%		Polynomial of component encoders & $[1 , 33/37 , 25/37]_8$\\
-	%		\hline
-	%	\end{tabular}
-	%	\end{center}
-	%\end{table}
 

### 2018-05-04 thread-pool-implementation/paper.tex
finished adding pics

@@
 In addition, we mixed the number of long and shorts tasks in each benchmark in order to generalize the real life scenario where a mixture of different tasks are executed.
-We want to show that the speedup is not or at least minimally affected by the type of tasks executed.\\
+We want to show that the speedup is not or at least minimally affected by the type of tasks executed.
+Then, we test the scalability of the thread pool itself by gradually increase the number of threads in the thread pool running $10,000$ tasks.
+The result matches with our expectation as the scalability is achieved when increasing the number of threads in the thread pool.\\
 
@@
 Dark Green: Goroutines}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:tf_plot}
+		\end{center}
+	\end{figure}
+
+\begin{figure}[!hbt]
+		% Center the figure.
+		\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{test_2.png}
+		% Create a subtitle for the figure.
+		\caption{Benchmark speedup using short blocking tasks and empty tasks.
+From left to right each section represents: long 25\% with short 75\%, long 50\% with short 50\%, and long 75\% with short 25\%.
+Green bar: pthread per task.
+Blue: Thread pool.
+Yellow: pthread per core.
+Dark Green: Goroutines}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:tf_plot}
+		\end{center}
+	\end{figure}
+
+\begin{figure}[!hbt]
+		% Center the figure.
+		\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{test_3.png}
+		% Create a subtitle for the figure.
+		\caption{Benchmark scalability of thread pool with $10,000$ tasks running. Threads used from left to right: $1$, $2$, $4$, $8$, $16$.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
@@
 
-\section{Conclusion}
-	This section summarizes the paper.
-
-% Now we need a bibliography:
-\begin{thebibliography}{5}
-
-	%Each item starts with a \bibitem{reference} command and the details thereafter.
-	\bibitem{HOP96} % Transaction paper
-	J.~Hagenauer, E.~Offer, and L.~Papke. Iterative decoding of binary block
-	and convolutional codes. {\em IEEE Trans. Inform. Theory},
-	vol.~42, no.~2, pp.~429–-445, Mar. 1996.
-
-	\bibitem{MJH06} % Conference paper
-	T.~Mayer, H.~Jenkac, and J.~Hagenauer. Turbo base-station cooperation for intercell interference cancellation. {\em IEEE Int. Conf. Commun. (ICC)}, Istanbul, Turkey, pp.~356--361, June 2006.
-
-	\bibitem{Proakis} % Book
-	J.~G.~Proakis. {\em Digital Communications}. McGraw-Hill Book Co.,
-	New York, USA, 3rd edition, 1995.
-
-	\bibitem{talk} % Web document
-	F.~R.~Kschischang. Giving a talk: Guidelines for the Preparation and Presentation of Technical Seminars.
-	\url{http://www.comm.toronto.edu/frank/guide/guide.pdf}.
-
-	\bibitem{5}
-	IEEE Transactions \LaTeX and Microsoft Word Style Files.
-	\url{http://www.ieee.org/web/publications/authors/transjnl/index.html}
-
-\end{thebibliography}
-
 % Your document ends here!

### 2018-05-04 thread-pool-implementation/paper.tex
done up to internal sync

@@
 % Define document title and author
-	\title{Thread Pool Implementation in C}
+	\title{JEThread: A Thread Pool Implementation in C}
 	\author{Jialin Li and Edward Hu}
@@
 \begin{abstract}
-	This is a short report on our thread pool performance.
+	JEThread is a Thread Pool written in C.
+It provides an easier interface and good performance for concurrent programming in C.
+JEThread achieves good performance across a mixture of workloads and automatically load balance through techniques like work stealing.
 \end{abstract}
@@
 	\PARstart{T}{hread} is a basic unit of CPU utilization, it consists of program counter, register set, and its own stack.
-Compared to processes, threads are much more lighweight since virtual memory space remains the same during a thread switch, which is not true for process switch.
+Compared to processes, threads are much more lightweight since virtual memory space remains the same during a thread switch, which is not true for process switch.
 However, even threads sometimes pose overhead that will affect the performance of the program.
 Initializing and cleaning threads can pose a certain amount of overhead.
-For an parallel application that creates and destroys a large number of threads that each only runs for a short time, the thread management mechanism can create unnecessary resource waste.
+For a concurrent application that creates and destroys a large number of threads that each only runs for a short time, the thread management mechanism can cause unnecessary resource waste.
 Thread pool can be useful in this type of scenario as it reduces the complexity of thread management and the overhead involved in thread creation and cleaning.
-The thread pool in implement in \textbf{GNU C}.
 
 % Main Part
+\section{Background}	
+	Without a thread pool, the common techniques used to do concurrent programming in C are to spawn a thread for each task, if task is long running, or to create a fixed number of worker threads and statically partition the work among the workers.
+Although both ways are feasible and provide control freedom to programmers, they can also be unnecessary burdens and require programmers to have a great deal of knowledge of both the workloads they are running and the type of thread programming model that  would result in good performance.
+Newer languages like Golang deals with this problem by providing Goroutines which are extremely lightweight user threads, as well as other concurrent native objects to better support concurrent programming.
+These features have brought Golang many users.
+For example, container engines like Docker and LXD, container orchestration tools like Kubernetes are all written in Golang.
+While it is hard to fully integrate runtime concurrent programming support in C, the thread pool abstraction provides a good middle ground.
+
 \section{Motivation}
-	We want to be able to implement a thread pool that is convinient to use.
-We aim to create a provide an interface that is easy for programmers to use.
-Thus we minimize the number of functions exposed to the programmers to maintain simplicity.
-We also want the performance of the thread pool to be reasonably more efficient than normal thread-based version.
-Thus we create several test cases to compare the performances in different implementations.
-We mainly focused on testing the performance difference in thread-based implementation and Goroutine-based version for certain types of jobs.
-Finally, we simply want to learn how to implement a thread pool and explore the drawbacks along with possible improvmetns.\\
-
-	There are several goals we are aiming to achieve in the experiment.
-First, we want to run both long and short tasks in the threal pool to analyze which type of tests have the most impact on the performance on the program.
-We've created created various tests for the thread pool to perform and we will show the data collected later in the analysis section.
-We hope the low overhead of switch between tasks will help us outperform thread-based implementation as well go-based implementation.
-In addition, we implemented work stealing mechanism to improve the work throughput done by the thread pool.
-We hope the work stealing function will further improve the efficiency of the thread pool.
+	Our primary goal is to implement a thread pool that is easy to use and flexible with different workloads.
+We minimizes the number of functions in the thread pool interface to keep it narrow yet fully functional.
+We also make a distinction between blocking and nonblocking tasks, and adopt techniques like work stealing to support various workloads.
+	We also want the thread pool to be reasonably more performant than previously mentioned pthread-based approaches.
+Thus we create several test cases to compare the performance in different implementations.
+Finally, we simply want to learn the inner-working of an efficient thread pool and explore the drawbacks along with possible improvements.\\
 
@@
 	\end{lstlisting}
-	This function initialize a new thread pool.
+	This function initializes a new thread pool.
 The \textbf{workers} attribute specifies the number of threads that can exist in a thread pool.
@@
 	\end{lstlisting}
-	This function signifies all threads in thread pool that no more job will be added and the calling function waits for all tasks in the thread pool to finish.
+	This function blocks until all threads in thread pool have finished all the existing jobs.
 		\end{itemize}
@@
 \section{Implementation}
-The low overhead of the thread pool is acheived with several design decisions.
-We will discuss the major implementations.
-A thread pool is first initialized by the main thread and the corresponding number of threads are initialized with their attributes.
+The low overhead of the thread pool is achieved with several design decisions. We will discuss the major implementations. 
+\subsection{Task Assignment}
 Each task is represented as a \textbf{struct task}.
-It is created by the calling function whenever the user sends the function to be executed to the thread pool.
-It is then distributed to the threads in the thread pool in a round-robin style to ensure even distribution.
+It is created by the calling function whenever the user sends the function to be executed to the thread pool and then distributed to the threads in the thread pool in a round-robin style to ensure even distribution.
+We keep track of the current worker that we are assigning to, and advance it after we've assigned $N$ tasks to it.
+This is to reduce the overhead of waking up workers when the number of tasks is few, and to try batching tasks and provide better tasks locality.
+This is based on the hypothesis that tasks created close in time are likely to reference similar memory regions.
+Therefore, we hope to keep them on the same worker thread.
+Even when this hypothesis does not hold, it does not hurt JEThread's performance.
+When a job is assigned to a worker, the main thread grabs the lock(spinlock suggested) to the worker's private queue and add it to the queue.
+
+In addition to batch assigning jobs, we also treat blocking and nonblocking tasks differently.
+This is necessary because JEThread by default starts with $N$ threads, where $N$ is the number of processors, and if all workers threads are executing some blocking tasks, then nonblocking tasks will not be able to execute until much later.
+It becomes even worse when majority of tasks are blocking tasks.
+In such case, the fixed number of workers would be blocked constantly.
+To solve this problem, we use an approach similar to Golang's parking threads, where we create a new thread to handle blocking tasks and only use our default set of worker threads to handle nonblocking tasks.
+In order to implement this, we need to identify if a task is blocking or nonblocking.
+This is difficult and inefficient to do at runtime, but can be done much easier in compile time.
+In our implementation, we rely on user to specify the CallType when adding a task.
+This is not fundamentally necessary - we could have modified GCC compiler or inspected task at preprocessing time to accomplish the same thing, but due to the time constraint we exposed this option to users.
+We believe that users would try their best to provide accurate CallType because they want better performance.
+Even if they accidentally misidentified CallType, this would not effect the correctness of JEThread.
+
+\subsection{Internal Synchronization}
 Each thread owns a privat task queue to store all its assigned tasks.
@@
 
-\section{Analysis}
+\section{Evaluation}
 Below is the hardware we used to conduct experiements on the performance of the thread pool.
@@
 	\end{table}
+
+There are several goals we are aiming to achieve in the experiment.
+First, we want to run both long and short tasks in the threal pool to analyze which type of tests have the most impact on the performance on the program.
+We've created created various tests for the thread pool to perform and we will show the data collected later in the analysis section.
+We hope the low overhead of switch between tasks will help us outperform thread-based implementation as well go-based implementation.
+In addition, we implemented work stealing mechanism to improve the work throughput done by the thread pool.
+We hope the work stealing function will further improve the efficiency of the thread pool.
 
@@
 \section{Conclusion}
-
-	% If you have questions about how to write mathematical formulas in LaTeX, please read a LaTeX book or the 'Not So Short Introduction to LaTeX': tobi.oetiker.ch/lshort/lshort.pdf
-
-	% This is how you include a eps figure in your document. LaTeX only accepts EPS or TIFF files.
-	\begin{figure}[!hbt]
-		% Center the figure.
-		\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{plot_tf}
-		% Create a subtitle for the figure.
-		\caption{Simulation results on the AWGN channel. Average throughput $k/n$ vs $E_s/N_0$.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:tf_plot}
-		\end{center}
-	\end{figure}
+	Write something here lol
 

### 2018-05-04 thread-pool-implementation/paper.tex
finish conclusion

--- 2018-05-04 thread-pool-implementation/paper.tex
@@
 			\hline
+			Compiler & GCC 5.40\\
+			\hline
 		\end{tabular}
@@
 \section{Conclusion}
+	Theoratically, thread pool can be very efficient especially dealing with a large number of relatively short tasks concurrently.
+In order to acheive maximum performance boost, the use of context switch should be minimized.
+The thread pool does a greate job of reducing the overhead in context switch.
+In addition, work stealing further facilitates the work throughput by letting idle threads execute other threads' tasks.
+However, thread pool is not a silver bullet that solves every problem of thread.
+The overhead of thread context switch is transfered to each thread's task queue as executing tasks requires dequeing the task each time, which also applies to job stealing.
+We've also conducted experiement with creating only one task queue shared between all threads, but the same thing still applies here that the overhead is transfered to the queue since accessing tasks is performed with lock's protection.
+In addition, round-robin style task distribution may not be the best way to distribute tasks as calling thread is unware of the actual workload in its distribution target.
+The work stealing is also very tricky to implement as the stealer is not aware of the workload distribution during runtime.
+If the majority of threads finish execution while a few survivor threads with many tasks are still alive, the parallelism can be compromised since a few threads become the bottleneck that causes main threads waiting unnecessarily.
+Additional improvements such that runtime dynamic workload check and compiler support for user-guided optimization will further increase the usibility of thread pool.\\
 
-	% If you have questions about how to write mathematical formulas in LaTeX, please read a LaTeX book or the 'Not So Short Introduction to LaTeX': tobi.oetiker.ch/lshort/lshort.pdf
-
-	% This is how you include a eps figure in your document. LaTeX only accepts EPS or TIFF files.
-	\begin{figure}[!hbt]
-		% Center the figure.
-		\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{plot_tf}
-		% Create a subtitle for the figure.
-		\caption{Simulation results on the AWGN channel. Average throughput $k/n$ vs $E_s/N_0$.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:tf_plot}
-		\end{center}
-	\end{figure}
+	In summary, the thread pool is great for running a large amount of tasks effciently with relatively small number of threads.
+In parallel applications with many short tasks to perform thread will be a strong candidate solution.
 

### 2018-05-04 thread-pool-implementation/paper.tex

--- 2018-05-04 thread-pool-implementation/paper.tex
@@
                         % at: http://www.ctan.org/tex-archive/info/
-\usepackage{xcolor}
+\usepackage{color}
 %\usepackage{psfrag}    % Written by Craig Barratt, Michael C. Grant,
@@
 The result matches with our expectation as the scalability is achieved when increasing the number of threads in the thread pool.\\
+
+\newpage
 
@@
 \section{Conclusion}
-	Write something here lol
+	Theoratically, thread pool can be very efficient especially dealing with a large number of relatively short tasks concurrently.
+In order to acheive maximum performance boost, the use of context switch should be minimized.
+The thread pool does a greate job of reducing the overhead in context switch.
+In addition, work stealing further facilitates the work throughput by letting idle threads execute other threads' tasks.
+However, thread pool is not a silver bullet that solves every problem of thread.
+The overhead of thread context switch is transfered to each thread's task queue as executing tasks requires dequeing the task each time, which also applies to job stealing.
+We've also conducted experiement with creating only one task queue shared between all threads, but the same thing still applies here that the overhead is transfered to the queue since accessing tasks is performed with lock's protection.
+In addition, round-robin style task distribution may not be the best way to distribute tasks as calling thread is unware of the actual workload in its distribution target.
+The work stealing is also very tricky to implement as the stealer is not aware of the workload distribution during runtime.
+If the majority of threads finish execution while a few survivor threads with many tasks are still alive, the parallelism can be compromised since a few threads become the bottleneck that causes main threads waiting unnecessarily.
+Additional improvements such that runtime dynamic workload check and compiler support for user-guided optimization will further increase the usibility of thread pool.\\
+
+	In summary, the thread pool is great for running a large amount of tasks effciently with relatively small number of threads.
+In parallel applications with many short tasks to perform thread will be a strong candidate solution.
 

### 2018-05-04 thread-pool-implementation/paper.tex
add more to implementation

--- 2018-05-04 thread-pool-implementation/paper.tex
@@
 
+\subsection{Blocking versus Non-Blocking Tasks}
 In addition to batch assigning jobs, we also treat blocking and nonblocking tasks differently.
@@
 Even if they accidentally misidentified CallType, this would not effect the correctness of JEThread.
+
+\subsection{Work Stealing}
+One of our goals is to achieve automatic load balancing.
+For this purpose, we implement work stealing for each worker thread.
+For each worker, we first do a sem\_trywait() to see if there is any job on its private queue.
+If there is none, then it randomly selects a victim thread and tries to steal a task from the victim and executes it.
+If keeps doing so until there is no more work to steal or if it has stolen $N$ times, where $N$ is the number of workers.
+This is our first attempt at work stealing.
+To optimize this, we could have kept randomly selecting victims until there is a victim with work above a certain threshold or up to a certain number of tries.
+To avoid all workers trying to steal when there is no tasks available, we can also use randomization to determine if a worker should try work stealing or just block until it is assigned a job.
+Another optimization we can perform is to steal more than one work at a time since we want it to be worth the overhead of running the algorithm.
+Although not reflected in the evaluation, we did try to evaluate the impact of the current work stealing techniques and found that even the naive approach improves the thread pool performance slightly.
 

### 2018-05-04 thread-pool-implementation/paper.tex

--- 2018-05-04 thread-pool-implementation/paper.tex
@@
 Even if they accidentally misidentified CallType, this would not effect the correctness of JEThread.
+
+\subsection{Work Stealing}
+One of our goals is to achieve automatic load balancing.
+For this purpose, we implement work stealing for each worker thread.
+For each worker, we first do a sem\_trywait() to see if there is any job on its private queue.
+If there is none, then it randomly selects a victim thread and tries to steal a task from the victim and executes it.
+If keeps doing so until there is no more work to steal or if it has stolen $N$ times, where $N$ is the number of workers.
+This is our first attempt at work stealing.
+To optimize this, we could have kept randomly selecting victims until there is a victim with work above a certain threshold or up to a certain number of tries.
+To avoid all workers trying to steal when there is no tasks available, we can also use randomization to determine if a worker should try work stealing or just block until it is assigned a job.
+Another optimization we can perform is to steal more than one work at a time since we want it to be worth the overhead of running the algorithm.
+Although not reflected in the evaluation, we did try to evaluate the impact of the current work stealing techniques and found that even the naive approach improves JEThread's performance slightly.
 

### 2018-05-04 thread-pool-implementation/paper.tex
put picture in proper position
adjustments on draft

@@
 \usepackage{color}
+\usepackage[section]{placeins}
 %\usepackage{psfrag}    % Written by Craig Barratt, Michael C. Grant,
@@
 	JEThread is a Thread Pool written in C.
-It provides an easier interface and good performance for concurrent programming in C.
+It provides an easy interface and good performance for concurrent programming in C.
 JEThread achieves good performance across a mixture of workloads and automatically load balance through techniques like work stealing.
@@
 	\PARstart{T}{hread} is a basic unit of CPU utilization, it consists of program counter, register set, and its own stack.
-Compared to processes, threads are much more lightweight since virtual memory space remains the same during a thread switch, which is not true for process switch.
-However, even threads sometimes pose overhead that will affect the performance of the program.
-Initializing and cleaning threads can pose a certain amount of overhead.
+Compared to processes, threads are much more lightweight since virtual memory space remains the same during a thread switch, which is not the case for process switch.
+However, even threads sometimes pose overhead that affects the performance of the program.
+Initializing and cleaning threads is one of the biggest contributors to the overhead.
 For a concurrent application that creates and destroys a large number of threads that each only runs for a short time, the thread management mechanism can cause unnecessary resource waste.
-Thread pool can be useful in this type of scenario as it reduces the complexity of thread management and the overhead involved in thread creation and cleaning.
+Thread pool can be useful in this type of scenario as it reduces the complexity of thread management and the overhead involved in thread creation and destruction.
 
@@
 \section{Background}	
-	Without a thread pool, the common techniques used to do concurrent programming in C are to spawn a thread for each task, if task is long running, or to create a fixed number of worker threads and statically partition the work among the workers.
-Although both ways are feasible and provide control freedom to programmers, they can also be unnecessary burdens and require programmers to have a great deal of knowledge of both the workloads they are running and the type of thread programming model that  would result in good performance.
+	Without a thread pool, the common techniques used to do concurrent programming in C are to spawn a thread for each task if it is long running, or to create a fixed number of worker threads and statically partition the work among the workers manually.
+Although both ways are feasible and provide control freedom to programmers, they can also add unnecessary burdens and require programmers to have a great deal of knowledge of both the workloads they are running and the type of thread programming model that would result in good performance.
 Newer languages like Golang deals with this problem by providing Goroutines which are extremely lightweight user threads, as well as other concurrent native objects to better support concurrent programming.
@@
 For example, container engines like Docker and LXD, container orchestration tools like Kubernetes are all written in Golang.
-While it is hard to fully integrate runtime concurrent programming support in C, the thread pool abstraction provides a good middle ground.
+While it is hard to fully integrate runtime concurrent programming support in C, the thread pool abstraction provides a good middle ground by providing easy programming model and efficency brought by C.
 
@@
 We minimizes the number of functions in the thread pool interface to keep it narrow yet fully functional.
-We also make a distinction between blocking and nonblocking tasks, and adopt techniques like work stealing to support various workloads.
+We also make a distinction between blocking and nonblocking tasks, and adopt techniques like work stealing to support various workloads.\\
 	We also want the thread pool to be reasonably more performant than previously mentioned pthread-based approaches.
@@
 The \textbf{workers} attribute specifies the number of threads that can exist in a thread pool.
-If $0$ is passd in, the number of threads will be initialized to the number of core in the execution environment.
+If $0$ is passd in, the number of threads will be initialized to the number of cores in the execution environment.
 The \textbf{mutex\_flag} argument let user decides whether to use mutex or spinlock as synchronization method.
-Note if the thread pool is initialized more than once, every invocation of this function will be discarded.\\
+Note if the thread pool is initialized more than once, every initialization after the first one will sinply be discarded.\\
 	\item 
@@
 the \textbf{CallType} specifies whether to use blocking or non-blocking mechanism for the thread pool.
-If a task is added without failure, $true$ is returned.
+If a task is added to thread pool without failure, $true$ is returned.
 Otherwise, $false$ will be returned.\\
@@
 	\end{lstlisting}
-	This function blocks until all threads in thread pool have finished all the existing jobs.
+	This function blocks until all threads in thread pool have finished all existing jobs.
 \end{itemize}
@@
 Each task is represented as a \textbf{struct task}.
-It is created by the calling function whenever the user sends the function to be executed to the thread pool and then distributed to the threads in the thread pool in a round-robin style to ensure even distribution.
+It is created by the calling function whenever the user sends a function to be executed to the thread pool and then the task is distributed to the threads in the thread pool in a round-robin style to ensure even distribution.
 We keep track of the current worker that we are assigning to, and advance it after we've assigned $N$ tasks to it.
@@
 Even when this hypothesis does not hold, it does not hurt JEThread's performance.
-When a job is assigned to a worker, the main thread grabs the lock(spinlock suggested) to the worker's private queue and add it to the queue.
+When a job is assigned to a worker, the main thread grabs the lock(spinlock suggested) to the worker's private queue and add it to the queue, then it signifies its target that new tasks are available by incrementing the target's semaphore.
 
@@
 In addition to batch assigning jobs, we also treat blocking and nonblocking tasks differently.
-This is necessary because JEThread by default starts with $N$ threads, where $N$ is the number of processors, and if all workers threads are executing some blocking tasks, then nonblocking tasks will not be able to execute until much later.
-It becomes even worse when majority of tasks are blocking tasks.
+This is necessary because JEThread by default starts with $N$ threads, where $N$ is the number of processors, and if all worker threads are executing some blocking tasks, then nonblocking tasks will not be able to execute until much later.
+It becomes even worse when the majority of tasks are blocking tasks.
 In such case, the fixed number of workers would be blocked constantly.
@@
 Another optimization we can perform is to steal more than one work at a time since we want it to be worth the overhead of running the algorithm.
-Although not reflected in the evaluation, we did try to evaluate the impact of the current work stealing techniques and found that even the naive approach improves JEThread's performance slightly.
+We evaluated the impact of the current work stealing techniques and found that even the naive approach improves JEThread's performance slightly compared to the implementation without work stealing.
 
 \subsection{Internal Synchronization}
-Each thread owns a privat task queue to store all its assigned tasks.
+Each thread owns a private task queue to store all its assigned tasks.
 Each queue is protected by either a mutex or a spinlock depending on users' specification.
@@
 Thus, we use semaphore to improve the efficiency of the thread pool.
-Thus we let the main thread invoking sema\_post on each thread once it finishes adding tasks to the thread's task queue to indicate the availability of tasks.
+We let the main thread invoking sema\_post on each thread once it finishes adding tasks to the thread's task queue to indicate the availability of tasks.
 However, the thread's task queue can be empty for other reasons.
 The most important one is that the thread finishes executing all assigned tasks.
-Thus, we implement work stealing algorithm to keep the idle thread busy by letting it trying to steal tasks from other threads by randomly choosing one.
+Thus, we implement work stealing algorithm to keep the idle thread busy by letting it try to steal tasks from other threads by randomly choosing one victim.
 Since we don't want tasks stealing to create too much overhead as it tries to grab tasks from other threads, we simply let the idle thread using pthread\_mutex\_trylock() or pthread\_spin\_trylock().
 If the stealing succeeds, the tasks is grabbed from the victim's task queue and executed.
-Otherwise, the steal will fail.
-If the steal fails too many times, that indicates many threads' task queue is already empty and the thread pool is getting close to running out of tasks.
+Otherwise, the steal will fail and the failure will be reported to the calling thread.
+If the steal fails too many times, that indicates many threads' task queue is either already empty and the thread pool is getting close to running out of tasks, or every victim is holding the lock.
+However, the possibility for the every victim to hold the thread just as the calling thread is trying to grab it is diminishing when more stealing are attempted.
 In this case, letting more threads trying to steal tasks will create unnecessary overhead, thus the thread will be blocked to prevent wasting resources.
-If eventually the threads run out of tasks, it will increase \textbf{wait\_sema} to let the main thread know it finishes its job.
+If eventually the threads run out of tasks, it will increase \textbf{wait\_sema} to let the main thread know that it finishes all its job.
 If all threads signify that they've finihsed their tasks, then thread pool is terminated.
@@
 First, we want to run both long and short tasks in the threal pool to analyze which type of tests have the most impact on the performance on the program.
-We've created created various tests for the thread pool to perform and we will show the data collected later in the analysis section.
-We hope the low overhead of switch between tasks will help us outperform thread-based implementation as well go-based implementation.
-In addition, we implemented work stealing mechanism to improve the work throughput done by the thread pool.
+We've created various tests for the thread pool to perform and we will show the data collected later in the analysis section.
+We hope the low overhead of switch between tasks will help us outperform thread-based implementation as well as go-based implementation.
+In addition, we implement work stealing mechanism to improve the work throughput done by the thread pool.
 We hope the work stealing function will further improve the efficiency of the thread pool.
@@
 We create same tasks for every implementation to execute to ensure fairness.
-we've selected three types of tests that represent three typical scenarios in most applications.
+We've selected three types of tests that represent three typical scenarios in most applications.
 We designed a task that accesses file system and performs read and write operations.
 Since accessing file system usually requires blocking which generates large overhead, this task is perfect to represent tasks that takes more than a few CPU cycles to finish.
-We also designed a task that task an argument, and then computer then sum based on the input and generates a simple hash value.
+We also designed a task that take in an argument, and the computer then performs sumation based on the input and generates a simple hash value.
 This represents a short to medium tasks present in most applications and we selected it as a candidate to represent short tasks.
 We also include a task that does nothing in order to test sheer performance of the thread pool without the influence of any outside factors.
-In addition, we mixed the number of long and shorts tasks in each benchmark in order to generalize the real life scenario where a mixture of different tasks are executed.
+In addition, we mixed the number of long and short tasks in each benchmark in order to generalize the real life scenario where a mixture of different tasks are executed.
 We want to show that the speedup is not or at least minimally affected by the type of tasks executed.
@@
 
-\newpage
+%\newpage
 
@@
 
+\FloatBarrier
+
 \section{Conclusion}

### 2018-05-04 thread-pool-implementation/paper.tex
on evaluation

--- 2018-05-04 thread-pool-implementation/paper.tex
@@
 For each worker, we first do a sem\_trywait() to see if there is any job on its private queue.
-If there is none, then it randomly selects a victim thread and tries to steal a task from the victim and executes it.
-If keeps doing so until there is no more work to steal or if it has stolen $N$ times, where $N$ is the number of workers.
+If there is none, then it randomly selects a victim thread.
+Since we don't want work stealing to create too much overhead as it tries to grab tasks from other threads, we first let the stealer try peeking at the victim's queue using pthread\_mutex\_trylock() or pthread\_spin\_trylock().
+If the stealing succeeds, a task is grabbed from the victim's task queue and executed.
+Otherwise, the steal will fail.
+If the steal fails too many times, that indicates many threads' task queue is already empty and the thread pool is getting close to running out of tasks.
+In this case, letting more threads trying to steal tasks will create unnecessary overhead, thus the thread will be blocked to prevent wasting resources.
+
 This is our first attempt at work stealing.
@@
 \subsection{Internal Synchronization}
-Each thread owns a privat task queue to store all its assigned tasks.
+Each worker thread owns a private task queue to store all its assigned tasks.
 Each queue is protected by either a mutex or a spinlock depending on users' specification.
-However, it is possible that a thread's task queue is empty when it is first initialized.
-It will waste CPU resource if such task is kept up and running without executing any tasks.
-Thus, we use semaphore to improve the efficiency of the thread pool.
-Thus we let the main thread invoking sema\_post on each thread once it finishes adding tasks to the thread's task queue to indicate the availability of tasks.
-However, the thread's task queue can be empty for other reasons.
-The most important one is that the thread finishes executing all assigned tasks.
-Thus, we implement work stealing algorithm to keep the idle thread busy by letting it trying to steal tasks from other threads by randomly choosing one.
-Since we don't want tasks stealing to create too much overhead as it tries to grab tasks from other threads, we simply let the idle thread using pthread\_mutex\_trylock() or pthread\_spin\_trylock().
-If the stealing succeeds, the tasks is grabbed from the victim's task queue and executed.
-Otherwise, the steal will fail.
-If the steal fails too many times, that indicates many threads' task queue is already empty and the thread pool is getting close to running out of tasks.
-In this case, letting more threads trying to steal tasks will create unnecessary overhead, thus the thread will be blocked to prevent wasting resources.
-If eventually the threads run out of tasks, it will increase \textbf{wait\_sema} to let the main thread know it finishes its job.
-If all threads signify that they've finihsed their tasks, then thread pool is terminated.
+We highly recommend using a spinlock because we've ran experiments for both types of locks and observed that the spinlock always provides better performance.
+This is because the critical section is small and the code design rarely leads to lock contention.
+
+In addition to preserving correctness through protected access to each worker's queue, we also try to keep JEThread's overhead low through efficient implementation.
+For example, when a worker runs out of tasks to execute, it can either busy wait or block.
+Because busy waiting will exhaust CPU resource, we decide to use a semaphore \textbf{task\_sema} to block a worker while there is no available task.
+When the main thread assigns tasks to the worker thread, it calls sema\_post on the worker's task\_sema.
+
+In order to wait for all worker threads to finish, in thread\_pool\_wait() we first mark each worker's private state \textbf{count} to true, then wake up each worker using \textbf{task\_sema} , and wait on each worker's \textbf{wait\_sema}.
+Once a worker wakes up, if there is no more job on its private queue and \textbf{count} is true, it wakes up the main thread to indicate that it has finished the current set of tasks.
 
@@
 There are several goals we are aiming to achieve in the experiment.
-First, we want to run both long and short tasks in the threal pool to analyze which type of tests have the most impact on the performance on the program.
-We've created created various tests for the thread pool to perform and we will show the data collected later in the analysis section.
-We hope the low overhead of switch between tasks will help us outperform thread-based implementation as well go-based implementation.
-In addition, we implemented work stealing mechanism to improve the work throughput done by the thread pool.
-We hope the work stealing function will further improve the efficiency of the thread pool.
+Firstly, we want to test the flexibility of the thread pool by running a mixture of long(blocking) and short tasks and evaluate how we perform compared to other implementations.
+Secondly, we want tot
 

### 2018-05-04 thread-pool-implementation/paper.tex

--- 2018-05-04 thread-pool-implementation/paper.tex
@@
 Another optimization we can perform is to steal more than one work at a time since we want it to be worth the overhead of running the algorithm.
-We evaluated the impact of the current work stealing techniques and found that even the naive approach improves JEThread's performance slightly compared to the implementation without work stealing.
+Although not reflected in the evaluation, we did try to evaluate the impact of the current work stealing techniques and found that even the naive approach improves JEThread's performance slightly.
 
 \subsection{Internal Synchronization}
-Each thread owns a private task queue to store all its assigned tasks.
+Each worker thread owns a private task queue to store all its assigned tasks.
 Each queue is protected by either a mutex or a spinlock depending on users' specification.
-However, it is possible that a thread's task queue is empty when it is first initialized.
-It will waste CPU resource if such task is kept up and running without executing any tasks.
-Thus, we use semaphore to improve the efficiency of the thread pool.
-We let the main thread invoking sema\_post on each thread once it finishes adding tasks to the thread's task queue to indicate the availability of tasks.
-However, the thread's task queue can be empty for other reasons.
-The most important one is that the thread finishes executing all assigned tasks.
-Thus, we implement work stealing algorithm to keep the idle thread busy by letting it try to steal tasks from other threads by randomly choosing one victim.
-Since we don't want tasks stealing to create too much overhead as it tries to grab tasks from other threads, we simply let the idle thread using pthread\_mutex\_trylock() or pthread\_spin\_trylock().
-If the stealing succeeds, the tasks is grabbed from the victim's task queue and executed.
-Otherwise, the steal will fail and the failure will be reported to the calling thread.
-If the steal fails too many times, that indicates many threads' task queue is either already empty and the thread pool is getting close to running out of tasks, or every victim is holding the lock.
-However, the possibility for the every victim to hold the thread just as the calling thread is trying to grab it is diminishing when more stealing are attempted.
-In this case, letting more threads trying to steal tasks will create unnecessary overhead, thus the thread will be blocked to prevent wasting resources.
-If eventually the threads run out of tasks, it will increase \textbf{wait\_sema} to let the main thread know that it finishes all its job.
-If all threads signify that they've finihsed their tasks, then thread pool is terminated.
+We highly recommend using a spinlock because we've ran experiments for both types of locks and observed that the spinlock always provides better performance.
+This is because the critical section is small and the code design rarely leads to lock contention.
+
+In addition to preserving correctness through protected access to each worker's queue, we also try to keep JEThread's overhead low through efficient implementation.
+For example, when a worker runs out of tasks to execute, it can either busy wait or block.
+Because busy waiting will exhaust CPU resource, we decide to use a semaphore \textbf{task\_sema} to block a worker while there is no available task.
+When the main thread assigns tasks to the worker thread, it calls sema\_post on the worker's task\_sema.
+
+In order to wait for all worker threads to finish, in thread\_pool\_wait() we first mark each worker's private state \textbf{count} to true, then wake up each worker using \textbf{task\_sema} , and wait on each worker's \textbf{wait\_sema}.
+Once a worker wakes up, if there is no more job on its private queue and \textbf{count} is true, it wakes up the main thread to indicate that it has finished the current set of tasks.
 
@@
 There are several goals we are aiming to achieve in the experiment.
-First, we want to run both long and short tasks in the threal pool to analyze which type of tests have the most impact on the performance on the program.
-We've created various tests for the thread pool to perform and we will show the data collected later in the analysis section.
-We hope the low overhead of switch between tasks will help us outperform thread-based implementation as well as go-based implementation.
-In addition, we implement work stealing mechanism to improve the work throughput done by the thread pool.
-We hope the work stealing function will further improve the efficiency of the thread pool.
+Firstly, we test the flexibility of the thread pool by running a mixture of long(blocking) and short tasks and evaluate how we perform compared to other implementations.
+Secondly, we evaluate the overhead of JEThread by running a mixture of short and empty tasks.
+The tasks we ran are common tasks in most web servers.
+The long task accesses file system, creates a file and writes 1106 bytes to the file.
+Since accessing file system usually requires blocking which generates large overhead, this task is perfect to represent tasks that takes lots of CPU cycles to finish.
+The short task generates a simple hash value and the empty task does nothing in order to test sheer overhead of the thread pool without the influence of any outside factors.
 
-We create same tasks for every implementation to execute to ensure fairness.
-We've selected three types of tests that represent three typical scenarios in most applications.
-We designed a task that accesses file system and performs read and write operations.
-Since accessing file system usually requires blocking which generates large overhead, this task is perfect to represent tasks that takes more than a few CPU cycles to finish.
-We also designed a task that take in an argument, and the computer then performs sumation based on the input and generates a simple hash value.
-This represents a short to medium tasks present in most applications and we selected it as a candidate to represent short tasks.
-We also include a task that does nothing in order to test sheer performance of the thread pool without the influence of any outside factors.
-In addition, we mixed the number of long and short tasks in each benchmark in order to generalize the real life scenario where a mixture of different tasks are executed.
-We want to show that the speedup is not or at least minimally affected by the type of tasks executed.
-Then, we test the scalability of the thread pool itself by gradually increase the number of threads in the thread pool running $10,000$ tasks.
+To show flexibility, we show that JEThread is able to outperform at least two other implementations despite of the workloads.
+We compared JEThread with pthread per core, pthread per task and Goroutines.
+Then, we test the scalability of JEThread by gradually increase the number of threads in the thread pool running $10,000$ short tasks.
 The result matches with our expectation as the scalability is achieved when increasing the number of threads in the thread pool.\\
@@
 \section{Conclusion}
-	Theoratically, thread pool can be very efficient especially dealing with a large number of relatively short tasks concurrently.
-In order to acheive maximum performance boost, the use of context switch should be minimized.
-The thread pool does a greate job of reducing the overhead in context switch.
-In addition, work stealing further facilitates the work throughput by letting idle threads execute other threads' tasks.
+	A thread pool should be efficient when managing a large number of tasks and executing them concurrently.
+In JEThread, we use work stealing to facilitate the work throughput by letting idle threads execute other threads' tasks.
 However, thread pool is not a silver bullet that solves every problem of thread.
-The overhead of thread context switch is transfered to each thread's task queue as executing tasks requires dequeing the task each time, which also applies to job stealing.
-We've also conducted experiement with creating only one task queue shared between all threads, but the same thing still applies here that the overhead is transfered to the queue since accessing tasks is performed with lock's protection.
-In addition, round-robin style task distribution may not be the best way to distribute tasks as calling thread is unware of the actual workload in its distribution target.
+The overhead of thread context switch is transferred to each thread's task queue as executing tasks requires dequeueing the task each time.
+We've also conducted experiment with creating only one task queue shared between all threads, but the same thing still applies here that the overhead is transferred to the queue since accessing tasks is performed with lock's protection.
+In addition, round-robin style task distribution may not be the best way to distribute tasks as calling thread is unaware of the actual workload in its distribution target.
 The work stealing is also very tricky to implement as the stealer is not aware of the workload distribution during runtime.
-If the majority of threads finish execution while a few survivor threads with many tasks are still alive, the parallelism can be compromised since a few threads become the bottleneck that causes main threads waiting unnecessarily.
-Additional improvements such that runtime dynamic workload check and compiler support for user-guided optimization will further increase the usibility of thread pool.\\
+If the majority of threads finish execution while a few survivor threads with many tasks are still alive, the parallelism can be compromised since a few threads become the bottleneck and cause the main thread waiting unnecessarily.
+Additional optimization such as runtime dynamic workload check and compiler support for user-guided optimization will further increase the usability of thread pool.\\
 
-	In summary, the thread pool is great for running a large amount of tasks effciently with relatively small number of threads.
+	In summary, the thread pool is great for running a large amount of tasks efficiently with relatively small number of threads.
 In parallel applications with many short tasks to perform thread will be a strong candidate solution.

### 2018-05-04 thread-pool-implementation/paper.tex
slight adjustment

--- 2018-05-04 thread-pool-implementation/paper.tex
@@
 If the majority of threads finish execution while a few survivor threads with many tasks are still alive, the parallelism can be compromised since a few threads become the bottleneck that causes main threads waiting unnecessarily.
-Additional improvements such that runtime dynamic workload check and compiler support for user-guided optimization will further increase the usibility of thread pool.\\
+Additional improvements such that runtime dynamic workload check and compiler support for user-guided optimization will further increase the usibility of thread pool.
 

### 2018-05-04 thread-pool-implementation/paper.tex

--- 2018-05-04 thread-pool-implementation/paper.tex
@@
 If the majority of threads finish execution while a few survivor threads with many tasks are still alive, the parallelism can be compromised since a few threads become the bottleneck and cause the main thread waiting unnecessarily.
-Additional optimization such as runtime dynamic workload check and compiler support for user-guided optimization will further increase the usability of thread pool.\\
+Additional optimization such as runtime dynamic workload check and compiler support for user-guided optimization will further increase the usability of thread pool.
 

### 2018-05-04 test.go
comment back in go test

@@ -27,7 +27,7 @@ proof-of-work chain as proof of what happened while they were gone. \n`
 func main() {
 	test_size := 1000
 
-	rate := 75
+	rate := 25
 	lnum_limit := test_size - rate*10
 	snum_limit := rate * 10
 	lnum := 0
@@ -86,18 +86,18 @@ func short_task(wg *sync.WaitGroup, num *int) {
 
 func long_task(wg *sync.WaitGroup, arg int) {
 	defer wg.Done()
-	// f, err := os.Create(fmt.Sprintf("goutput/tmp-%d", arg))
-	// if err != nil {
-	// 	fmt.Println("Failed to create")
-	// 	return
-	// }
+	f, err := os.Create(fmt.Sprintf("goutput/tmp-%d", arg))
+	if err != nil {
+		fmt.Println("Failed to create")
+		return
+	}
 
-	// wsize, err := f.WriteString(data)
-	// if err != nil {
-	// 	fmt.Println("Failed to write string")
-	// 	return
-	// }
-	// if wsize < len(data) {
-	// 	fmt.Printf("Failed to write all data expected %v, written %v \n", len(data), wsize)
-	// }
+	wsize, err := f.WriteString(data)
+	if err != nil {
+		fmt.Println("Failed to write string")
+		return
+	}
+	if wsize < len(data) {
+		fmt.Printf("Failed to write all data expected %v, written %v \n", len(data), wsize)
+	}
 }

### 2018-05-04 test.go
add changes to go test

@@ -3,7 +3,7 @@ package main
 import (
 	"fmt"
 	"math/rand"
-	// "os"
+	"os"
 	"sync"
 	"time"
 )
